\noindent \textsc{\Large Acknowledgements} \\
\hrule
\vspace{5mm}
\doublespacing

I would like to first acknowledge Professor T. V. RajanBabu of The Ohio State University, for my
development as an organic chemist undoubtedly began in his laboratories as a young undergraduate
student. Professor RajanBabu, through his lectures and our discussions, instilled within me a great
sense of scientific virtue and rigor that I will carry with me for the rest of my life. It was
through his suggestion that I ended up applying for graduate school at Boston College.


At Boston College I have been fortunate to have worked with a number of distinguished faculty
members. Professor Jason Kingsbury has been, and continues to be a strong source of support as I
move forward with my career. As an advisor, Jason gave me a tremendous amount of intellectual
freedom and provided the environment and encouragement for my ideas to grow. He has an incredible
sense of compassion for his students and has always wanted the best for us. Professor Kian Tan,
through his own actions, taught me the importance of determination and hard work. Professor Lawrence
Scott has always been available to assist me with chemistry or publications to no benefit of his
own, and for that I am grateful. Professor Marc Snapper has a brilliant and unique perspective on
chemistry and learning from his approach has been an important part of my development as a
scientist. Professor Amir Hoveyda has a contagious sense of enthusiasm for chemistry and I feel
fortunate to have worked with him.


I would also like to thank all of the graduate and undergraduate students who have made my time at
Boston College more enjoyable. I have been very fortunate to have met several people in particular
through this process who have enriched my life in many ways. Hilan Kaplan is an exceptionally
skilled and passionate scientist who I have learned a great deal from through our discussions and
from working together. Hilan has been an incredible friend and we had a lot of fun together in the
Kingsbury lab. I was also lucky to have the opportunity to work with Bowman Potter, who has become a
great friend as well. My time spent in the Snapper lab was more enjoyable because of Bowman, and his
dedication was inspirational towards the end of my graduate career. In the Kingsbury and Snapper
labs we never had a lot of resources, but with both Hilan and Bowman, we were able to work as a
close team and accomplish far more than what we ever could have done individually.


Finally, I would like to acknowledge a very special relationship with Samantha Goetz that has had a
profound impact on my life over the past few years. Samantha is a highly competent and conscientious
chemist who is always thinking and asking the right questions. Her curiosity has forced me
reevaluate many aspects of chemistry where I had since become complacent. Outside of the lab,
Samantha is one of the most compassionate people I have ever encountered. I am forever indebted to
her love and support, which has helped make this work possible.



